### 2019-02-10 paper.tex
Wip

\newcommand{\theHalgorithm}{\arabic{algorithm}}

@@

\vskip 0.3in

\begin{abstract}
  Guild AI is an open souce tool for running, tracking, and comparing
  machine learning experiments. Guild helps researchers and engineers
  do their work more efficiently without imposing additional
  configuration and system requirements. By simplifying experiment
  tracking, Guild hopes to encourage more consistent reproducibility
  and improved collaboration in machine learning research.
\end{abstract}
]

@@

Guild AI is a command line tool that runs researcher code without
modification. It automatically captures runs as unique experiments and
provides facilities to analyze, compare, and share results.

\textbf{Experiments.} Guild runs experiment trials as operating system
processes and tracks results in separate run directories. Each run
directory contains artifcats generated during the trial along with
metadata such as model information, start and stop times, logs, and
run status. Run artifacts commonly include training checkpoints,
prepared data sets, generated content such as images and audio, logs,
and project source code snapshots.

\textbf{Analysis.} Guild provides facilities to analyze and compare
experiments. User study experiment outputs such as training and
validation loss, accuracy, required memory, batch latency---any metric
recorded across experiments---as well logs and generated files. Guild
also supports detailed comparison across experiment inputs including
changes in model architecture, hyperparameters, data sets, and source
code.

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item Users \emph{publish experiment results} to remote locations over
  SSH or cloud services like S3 where they are studied and compared by
  others.

\item Project maintainers use \emph{Guild files}---simple YAML files
  included with project source---to document and automate project
  capabilities such as supported models, operations, hyperparameter
  defaults and search space for optimization experiments.

\item Project maintainers may further generated Python \emph{packages}
  that are uploaded to PyPI and installed by others for reproducing
  results.
\end{itemize}

\textbf{Command Line Interface, Visualization, API.} Guild's primary
user interface is a command line interface, which integrates
efficiently with other system tools. Guild additionally provides a
graphical, web based dashboard to explore and analyze runs and
integration with TensorBoard. Guild exposes functionality in a Python
API for application developers.

\textbf{Cross Framework and Language Support.} Guild supports any
learning script that generates experiment results. Models may be
implemented in any language, framework, or software library. Commonly
supported libraries include TensorFlow, Keras, PyTorch, MXNet,
scikit-learn, and SGBoost. However, Guild supports other Python
libraries, pure Python, and languages such as R, Go, and Java.

@@

Guild facilitates reproducibility across trials by capturing results
and providing tools for comparison. A typical workflow in Guild is:

\begin{enumerate}[noitemsep, topsep=0pt, partopsep=0pt]
\item Run trials for a baseline model
\item Run trials for novel work
\item Compare and analyze results
\end{enumerate}

Guild additionally supports packaging work for distribution for others
to install and run trials to serve as baselines for their work.

@@

Guild is used by researchers and engineers to run, track, and compare
machine learning experiments. It is useful to anyone who outinely runs
experiments that compare novel work to baseline results.

@@

Each requirement that a tool imposes on a user adds friction to the
process of experiment automation and tracking. Researchers may
perceive the cost of reproducibility to be greater than the benefits.

To encourage systematic machine learning, Guild does not require
changes to user code or installation and maintenance of external
systems. Users run their training scripts without modification. For
example, an unmodified Python script \texttt{train.py} that supports
hyperparameters \texttt{n\_layers} and \texttt{lr} may be run using:

@@

With this command, the user generates a unique experiment with the
specified hyperparameters that can be analyzed and compared to other
trials. Guild supports this workflow without external dependencies.

@@

We propose an interactive scenario that highlights the benefits of
fast, easy experiment reproduction. During the demo, he presenter
refers to two personas---represented visually with placards---to help
viewers maintain context as stages of the scenario are presented:

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Arya}. A researcher who has published state-of-the-art
  results of a novel architecture on a standard benchmark dataset.
\item \emph{Clegane}. A researcher working on a survey paper that
  includes Arya's work.
\end{itemize}

While demonstrating a scenario, the presenter will highlight how Guild
supports reproducibility in two areas:

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Influence}. Work that is easier to reproduce is more
  likely to influence others (other factors held constant).

\item \emph{Productivity}. Tools that simplify and speed
  reproducibility are applied equally to trial generation in general.
  Researchers can learn from more experiments in less time to improve
  results.
\end{itemize}

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Arya} uses Guild to run training and validation
  experiments, collecting results---both positive and negative---and
  announces her findings in a celebrated invited talk at SysML. Her
  work is automatically reproducibile when she commits her code to
  GitHub.

@@

\item \emph{Arya} pulls Clegane's results from S3 and uses Guild to
  study the differences between her results and Clegane's. She uses
  this information to answer Clegane's questions.

\item \emph{Clegane}, to promote his field of study and encourage
  further research, creates an installable package that others use to
  reproduce Arya's work along with his own findings.
\end{itemize}

>>>>

@@

\vskip 10pt

\begin{abstract}
  Guild AI is an open source tool for running, tracking, and comparing
  machine learning experiments. Guild helps researchers and engineers
  do their work more efficiently without imposing additional
  configuration and system requirements. By simplifying experiment
  tracking, Guild hopes to encourage more consistent reproducibility
  and improved collaboration in machine learning research.
\end{abstract}
]

@@

\textbf{Experiments.} Guild runs experiment trials as operating system
processes and tracks results in separate run directories. Each run
directory contains artifacts created during the trial along with
metadata such as model information, start and stop times, logs, and
run status. Run artifacts commonly include training checkpoints,
prepared data sets, generated content such as images and audio, logs,
and project source code snapshots.

\textbf{Analysis.} Guild provides facilities to analyze and compare
experiments. Users can study experiment outputs such as training and
validation loss, accuracy, required memory, batch latency as well logs
and generated files. Guild also supports detailed comparison across
experiment inputs including changes in model architecture,
hyperparameters, data sets, and source code.

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item Project maintainers use \emph{Guild files}---simple YAML files
  included with project source---to document and automate project
  capabilities such as supported models, operations, hyperparameter
  defaults and search space for optimization experiments.

\item Project maintainers create Python \emph{packages} that are
  uploaded to PyPI and installed by others for reproducing results.

\item Users \emph{publish experiment results} to remote locations over
  SSH or cloud services like S3 where they are securely studied and
  compared by others.
\end{itemize}

\textbf{Command Line Interface, Visualization, API.} Guild's primary
user interface is a command line interface, which integrates
efficiently with other system tools. Guild additionally provides a
graphical, web based dashboard to explore and analyze runs and
integration with TensorBoard. Guild also exposes functionality in a
Python API for application developers.

\textbf{Cross Framework and Language Support.} Guild supports any
learning script that generates experiment results. Models may be
implemented in any language, framework, or software library.

@@

Guild facilitates reproducibility by automating experiments,
systematically capturing results, and providing tools for analysis and
comparison. A typical workflow in Guild is:

\begin{enumerate}[noitemsep, topsep=0pt, partopsep=0pt]
\item Run trials for a baseline model
\item Run trials for novel work
\item Compare and analyze results
\item Optionally package and distribute project code to further
  simplify reproducibility
\end{enumerate}

@@

Guild is used by researchers and engineers to run, track, and compare
machine learning experiments. It is useful to anyone who needs to
compare novel work to baseline results.

@@

Each requirement that a tool imposes on a user presents a barrier to
the goal of systematic machine learning. In some cases, researchers
may view the cost of automation in support reproducibility to
outweight the benefit.

To encourage systematic machine learning, Guild does not require
changes to user code or installation and maintenance of external
systems. Users run their training scripts without modification. For
example, an unmodified Python script \texttt{train.py} that supports
hyperparameters \texttt{n\_layers} and \texttt{lr} may be run using a
command such as:

@@

With this command, the user generates a unique experiment with the
specified hyperparameters, which can be analyzed and compared to other
trials.

Guild supports this workflow without external dependencies.

@@

We propose an interactive demonstration that highlights the benefits
of fast, easy experiment reproduction. Throughout the session, the
presenter refers to two personas---represented visually with
placards---to help viewers maintain context for various scenario:

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Arya}. A researcher who has published state-of-the-art
  results of a novel architecture on a standard benchmark data set.
\item \emph{Clegane}. A researcher working on a survey paper that
  includes Arya's work.
\end{itemize}

While demonstrating a scenario, the presenter highlights how Guild
supports reproducibility in two areas:

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Influence}. Work that is easier to reproduce is more
  likely to influence others, other factors held constant.

\item \emph{Productivity}. Tools that support fast and easy
  reproducibility are applicable to research in general: more
  experiments generate more data, which researchers can use to advance
  their work.
\end{itemize}

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Arya} uses Guild to run training and validation
  experiments, collecting results---both positive and negative---and
  announces her findings in a celebrated invited talk at SysML. Her
  work is fully reproducible when she commits her code to GitHub.

@@

\item \emph{Arya} pulls Clegane's results from S3 and uses Guild to
  study the differences between her results and Clegane's and uses
  this information to answer his questions.

\item \emph{Clegane}, to promote his field of study and encourage
  further research, creates an installable package that others can use
  to reproduce Arya's work along with his own findings.
\end{itemize}
